Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-09 minimax.tex

\noindent The candidate questions to the chair are determined as in the Random strategy.
The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile'_1, W'_1)$, depending on the answer. 
Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers depending on the kind of question; these parameters are to be determined experimentally and are use to fine control the choice of the question type.
Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
We are now faced with the problem of aggregating these values to determine the informative value of the question. Motivated by  \citet{Cailloux2014} we adopt a pessimistic approach, reported to perform much better than optimistic aggregation.
% use this operator, similar to a $\max$ operator, because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
However, to avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
Pessimistic considers question $q_1$ to be better  than $q_2$ iff
\begin{align}
	R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2].
\end{align}
%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
%The motivation for using this operator lies in 
In other words if the maximal {\em a posteriori} $\MMR$ of two questions are (nearly) equal, then it considers the (penalized) minimal $\MMR$ values, preferring the question with the lowest value.
(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal $\MMR$ values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal $\MMR$.)

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
%MMR and sd with systematically one decimal exactly
%\end{enumerate}

Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.

Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. The weights are generated by drawing $m-1$ differences randomly with uniform distribution, normalizing them, then ordering them, in order to ensure convexity.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$ and $\epsilon'_{\text{chair}} = 10^{-6}$ and $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.

We start with empty knowledge ($\pprofile = (\emptyset, \emptyset, …), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair. We obtain the first question to be asked using the strategy under test, as described above. We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question. This is repeated until $k$ answers have been obtained, compute the resulting $\MMR$ values along the way for various values of $k$. We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation \textit{sd}.

>>>>

\noindent The candidate questions to the chair are determined as in the Random strategy.
The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile'_1, W'_1)$, depending on the answer. 
Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are to be determined experimentally and are used to fine control the choice of the question type.
Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
We are now faced with the problem of aggregating these values to determine the informative value of the question. Motivated by  \citet{Cailloux2014} we adopt a pessimistic approach, reported to perform much better than optimistic aggregation.
% use this operator, similar to a $\max$ operator, because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
However, to avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
Pessimistic considers question $q_1$ to be better  than $q_2$ iff
\begin{align}
	R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2].
\end{align}
%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
%The motivation for using this operator lies in 
In other words if the maximal {\em a posteriori} $\MMR$ of two questions are (nearly) equal, then it considers the (penalized) minimal $\MMR$ values, preferring the question with the lowest value.
(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal $\MMR$ values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal $\MMR$.)

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
%MMR and sd with systematically one decimal exactly
%\end{enumerate}
We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies. %Our experiments are described by topic here below. 
We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. 
For gerenerating the weights we first draw $m-1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
a sequence of convex decreasing weight is then obtained by a decumulative sum.% to the former numbers.
% ordering them, in order to ensure convexity.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$ and $\epsilon'_{\text{chair}} = 10^{-6}$ and $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.

We start with empty knowledge ($\pprofile = (\emptyset, \emptyset, …), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair. We obtain the first question to be asked using the strategy under test, as described above. We then use the oracle to answer the question and update the system's knowledge, which is thus used to obtain the next question. This is repeated until $k$ answers have been obtained, computinh the resulting $\MMR$ values along the way for various values of $k$. We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation \textit{sd}.
